Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
Jessie updating related works

\subsection{Related works}
A brief history of the convex surrogate.
\begin{itemize}
  \item \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
  \item \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
  This paper evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization. \jessie{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
  \item \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.

  \item \cite{ramaswamy2018consistent} \jessie{Originally in 2014... new version in 2018.} is the first paper, to our knowledge to prove bounds on the elicitation complexity of the abstain property.
  They shouw that the abstain property with $\alpha = 1/2$ can be elicited by a convex surrogate in $\ceil*{\log_2 n}$ dimensions.
  However, it remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that their bound is tight, at least from the perspective from embedding.
  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate.
  \item \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our ``embedded property'' that we actually elicit by a convex surrogate in lieu of directly eliciting a finite (i.e. classification, ranking) property.
  However, they do not think of properties as set-valued, leading to a less rigorous treatment and understanding of the link.
  Most of their results focus on linear properties \jessie{is there a relationship between linear and orderable properties?}

  \item \cite{ramaswamy2016convex} discusses and formalizes the notion of \emph{convex calibration} dimension for finite properties.
  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
  In this paper, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
  This method can be applied to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property.
  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
\end{itemize}

>>>>

\subsection{Related works}
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.

  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}

%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.

  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.

  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works, to our knowledge, that generalizes the construction of convex surrogates beyond the binary outcome setting comes from~\cite{ramaswamy2018consistent}-- originally appearing in 2014. 
  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.

  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}

  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
